Secure Composition of Robust and Optimising Compilers

### 2023-06-20 popl/main.tex
Program behaviour

>>>>

\begin{center}
  \judgbox{\progstepto{\prog{\library_{\ctx}}{\library_{\comp}}}{\runtimetermvar}{\trace}}{,,Program $\prog{\library_{\ctx}}{\library_\comp}$ evaluates to $\runtimetermvar$, emitting trace $\trace$.''}
  %
  \typerule{ep-run}{
    \link{\library_{\ctx}}{\library_{\comp}}=\library &
    \commlib=\operatorname{dom}\library_{\comp} \\
    \estepto{\rtt{\tup{\library}{\commlib,\emptyset}}{\lcall{\text{main}}{0}}}{\rtt{\statevar}{\valueexpr}}{\trace}
  }{
    \progstepto{\prog{\library_{\ctx}}{\library_{\comp}}}{\rtt{\statevar}{\valueexpr}}{\trace}
  }{ep-run}
  %
  \typerule{ep-crash}{
    \link{\library_{\ctx}}{\library_{\comp}}=\library &
    \commlib=\operatorname{dom}\library_{\comp} \\
    \estepton{\rtt{\tup{\library}{\commlib,\emptyset}}{\lcall{\text{main}}{0}}}{\lightning}{\trace\cdot\lightning}
  }{
    \progstepto{\prog{\library_{\ctx}}{\library_{\comp}}}{\lightning}{\trace\cdot\lightning}
  }{ep-crash}
\end{center}

The notation $\tup{\library}{\commlib,\emptyset}$ unfolds to $\statevar=\tup{\cfstate}{\comp,\memstate}$, where $\cfstate=\tup{\library}{\commlib,\hole{\cdot}}$ and $\memstate=\tup{\hole{\cdot}}{\hole{\cdot},\hole{\cdot}}$.
Linking $\link{\library_{\ctx}}{\library_{\comp}}$, while gluing $\library_{\ctx}$ and $\library_{\comp}$ together, ensures that there is no symbol with the name $\text{main}$ in $\library_{\comp}$.
Programs can either be run successfully (\Cref{tr:ep-run}) or fail (\Cref{tr:ep-crash}), which requires the n-step relation instead of star step, since star step models a big--step style semantics without failure.
To make use of \Cref{def:propsat,def:proprsat}, {\em behavior} is introduced as follows.

\begin{definition}[Program Behavior]\label{def:behav}
  Given a program $\prog{\library_{\ctx}}{\library_{\comp}}$, the behavior of it is a set containing all traces $\trace$ such that there is a runtime--term $\runtimetermvar$ with $\progstepto{\prog{\library_{\ctx}}{\library_{\comp}}}{\runtimetermvar}{\trace}$.
\end{definition}
